% epubtoolsCommandlineepubU-De.tex
\begin{hcarentry}[updated]{epub-tools (Command-line epub Utilities)}
\label{epubtools}
\report{Dino Morelli}%11/11
\status{stable, actively developed}
\makeheader

A suite of command-line utilities for creating and manipulating epub book files. Included are: epubmeta, epubname, epubzip.

epubmeta is a command-line utility for examining and editing epub book metadata. With it you can export, import and edit the raw OPF Package XML document for a given book. Or simply dump the metadata to stdout for viewing in a friendly format.

epubname is a command-line utility for renaming epub ebook files based on their OPF Package metadata. It tries to use author names and title info to construct a sensible name. epubname has recently undergone extensive redesign:

- Major change of the formatting rules system. Renaming machinery is now described in a domain-specific language, NOT in statically compiled code. Users are able to extend the functionality with custom naming rules in conf files.

- Added interactive mode to ask about each file rename as they happen, this is like darcs now!

- Added ability to specify target directory for books to be moved to as part of renaming.

epubzip is a handy utility for zipping up the files that comprise an epub into an .epub zip file. Using the same technology as epubname, it can try to make a meaningful filename for the book.

epub-tools is available from Hackage and the Darcs repository below.

\FurtherReading
\begin{compactitem}
\item Project page:
\url{http://ui3.info/d/proj/epub-tools.html}

\item Source repository:
\texttt{darcs get} \url{http://ui3.info/darcs/epub-tools}
\end{compactitem}
\end{hcarentry}
